---
title: "CoinATMRadar KC Database Creation"
output: html_notebook
---

```{r setup}
#Libraries
library(httr)
library(tidyverse)
library(janitor)
library(rvest)
library(ggmap)
```

```{r}
#Below is the Powershell command to rename the HTMLs from their site names to R-friendly file names

#PS C:\Users\danmi\Desktop\KC_Crypto_HTMLs> $files = Get-ChildItem
#>> $count = 1
#>> foreach ($file in $files) {
#>>     $newName = "{0:D3}" -f $count   # Rename files with zero-padded 4-digit numbers
#>>     $file | Rename-Item -NewName "$newName.html"
#>>     $count++
#>> }
```

Initial scrape.
```{r}
# Set the directory path where the files are located
directory <- "C:/Users/danmi/Documents/GitHub/KCCryptoATMs/KC_Crypto_HTMLs"

# Create an empty tibble to store the results
results <- tibble()

# Create loop
for (i in 1:181) {
  # Target file names
  filename <- sprintf("%03d.html", i)
  
  # Construct the complete file path by concatenating the directory and file name
  filepath <- file.path(directory, filename)
  
  # Load HTML
  html <- read_html(filepath)

  # Description tag carries Business Name and ATM Brand
  description <- html %>% html_nodes('h1') %>% html_text() %>% as.character()

  # Address (Somewhat messy, need to check CSS again)
  address <- html %>%  html_nodes(xpath = '//meta[10]') %>% html_attr('content') %>% as.character()
    if (length(address) == 0) {
    address <- rep(NA, length(description))
  }
  
  # Install date (.date)
  install_date <- html %>% html_elements(".date") %>% html_text() %>% as.character()
    if (length(install_date) == 0) {
    install_date <- rep(NA, length(description))
  }

  # Operator Name
  operator_name <- html %>% html_elements("#atm-operator-logo+ p a") %>% html_text2() %>% as.character()
  if (length(operator_name) == 0) {
    operator_name <- rep(NA, length(description))
  }
  
    # Operator Name
  cryptos_offered <- html %>% html_elements("tr:nth-child(3) td:nth-child(1) , tr:nth-child(8) td:nth-child(1) , tr:nth-child(6) td:nth-child(1) , tr:nth-child(7) td:nth-child(1) , tr:nth-child(9) td:nth-child(1) , tr:nth-child(10) td:nth-child(1) , tr:nth-child(11) td:nth-child(1) , tr:nth-child(12) td:nth-child(1) , tr:nth-child(5) td:nth-child(1) , tr:nth-child(4) td:nth-child(1) , tr:nth-child(2) td:nth-child(1)") %>% html_text2() %>% as.character()
  if (length(operator_name) == 0) {
    operator_name <- rep(NA, length(description))
  }
  
 #Temp tibble for loop results
  temp_tibble <- tibble(File = filename, Description = description, Address = address, Install_Date = install_date, Operator_Name = operator_name, Cryptos = cryptos_offered)
  
  #Merge temp tibble to main tibble
  results <- bind_rows(results, temp_tibble)
}

#write.csv(results, "C:\\Users\\danmi\\Desktop\\KC_Crypto_1.csv", row.names=TRUE)
```

Combine cryptos offered into one column.
```{r}
crypto_offered <-  aggregate(Cryptos ~ File, data = results, FUN = function(x) paste(unique(x), collapse = ", "))
crypto_offered <- mutate(crypto_offered, Cryptos = str_remove(Cryptos, ", Supported fiat:"))
```

Modify results to append cryptos
```{r}
results <- results %>% select(-Cryptos)
results <- results %>% distinct(File, .keep_all = TRUE)
results <- left_join(results, crypto_offered, by = "File")
```


Create a loop to pull alerts. This gets its own section because the loops as is spit out duplicate rows for files that do carry an .alert tag.
```{r}
# Set the directory path where the files are located
directory <- "C:/Users/danmi/Documents/GitHub/KCCryptoATMs/KC_Crypto_HTMLs"

# Create an empty tibble to store the results
alert_results <- tibble()

# Create loop
for (i in 1:181) {
  # Target file names
  filename <- sprintf("%03d.html", i)
  
  # Construct the complete file path by concatenating the directory and file name
  filepath <- file.path(directory, filename)
  
  # Load HTML
  html <- read_html(filepath)

  # Alert? (p.alert)
  alert <- html %>% html_elements(".alert") %>% html_text()
  if (length(alert) == 0) {
    alert <- NULL
  }
  
 #Temp tibble for loop results
  alert_temp <- tibble(File = filename, Alert = alert)
  
  #Merge temp tibble to main tibble
  alert_results <- bind_rows(alert_results, alert_temp)
}

#The output of the loop binds the temp tibble, which lists every item in the database, against the results, which just extracts those with the alert tag. Delete these duplicates.

alert_results <- alert_results %>% distinct(File, .keep_all = TRUE)
```

Merge tables.
```{r}
complete_results <- left_join(results, alert_results, by = "File")
```


Cleaning time.
```{r}
#Remove "installed on", standardize dates
complete_results <- mutate(complete_results, Install_Date = str_remove(Install_Date, "Installed on"))
complete_results <- mutate(complete_results, Install_Date = mdy(Install_Date))

#Remove intro to isolate addresses
complete_results <- mutate(complete_results, Address = str_remove(Address, ".* at"))

#Add comma separator between street name and city
complete_results <- mutate(complete_results, Address = str_replace(Address, "Ave<br />", "Avenue, "))
complete_results <- mutate(complete_results, Address = str_replace(Address, "Ave.<br />", "Avenue, "))
complete_results <- mutate(complete_results, Address = str_replace(Address, "Blvd<br />", "Boulevard, "))
complete_results <- mutate(complete_results, Address = str_replace(Address, "Blvd.<br />", "Boulevard, "))
complete_results <- mutate(complete_results, Address = str_replace(Address, "Boulevard<br />", "Boulevard, "))
complete_results <- mutate(complete_results, Address = str_replace(Address, "Broadway<br />", "Broadway, "))
complete_results <- mutate(complete_results, Address = str_replace(Address, "Cutoff<br />", "Cutoff, "))
complete_results <- mutate(complete_results, Address = str_replace(Address, "Drive<br />", "Drive, "))
complete_results <- mutate(complete_results, Address = str_replace(Address, "Dr<br />", "Drive, "))
complete_results <- mutate(complete_results, Address = str_replace(Address, "Dr.<br />", "Drive, "))
complete_results <- mutate(complete_results, Address = str_replace(Address, "Highway<br />", "Highway, "))
complete_results <- mutate(complete_results, Address = str_replace(Address, "HWY<br />", "Highway, "))
complete_results <- mutate(complete_results, Address = str_replace(Address, "Ln<br />", "Lane, "))
complete_results <- mutate(complete_results, Address = str_replace(Address, "Parkway<br />", "Parkway, "))
complete_results <- mutate(complete_results, Address = str_replace(Address, "Pkwy<br />", "Parkway, "))
complete_results <- mutate(complete_results, Address = str_replace(Address, "St<br />", "Street, "))
complete_results <- mutate(complete_results, Address = str_replace(Address, "St.<br />", "Street, "))
complete_results <- mutate(complete_results, Address = str_replace(Address, "st<br />", "Street, "))
complete_results <- mutate(complete_results, Address = str_replace(Address, "S<br />", ", "))
complete_results <- mutate(complete_results, Address = str_replace(Address, "Street<br />", "Street, "))
complete_results <- mutate(complete_results, Address = str_replace(Address, "Rd<br />", "Road, "))
complete_results <- mutate(complete_results, Address = str_replace(Address, "Rd.<br />", "Road, "))
complete_results <- mutate(complete_results, Address = str_replace(Address, "Road<br />", "Road, "))
complete_results <- mutate(complete_results, Address = str_replace(Address, "Terrace<br />", "Terrace, "))
complete_results <- mutate(complete_results, Address = str_replace(Address, "Paseo<br />", "Paseo, "))
complete_results <- mutate(complete_results, Address = str_replace(Address, "Trafficway<br />", "Trafficway, "))
#(\\d+) targets any numbers, \\1 tells R to keep the number in place once applying the formatting.
complete_results <- mutate(complete_results, Address = str_replace(Address, "Lot (\\d+)", "Lot \\1, "))
complete_results <- mutate(complete_results, Address = str_replace(Address, "Hwy (\\d+)", "Highway \\1, "))
complete_results <- mutate(complete_results, Address = str_replace(Address, "Suite (\\d+)", "Suite \\1, "))
complete_results <- mutate(complete_results, Address = str_replace(Address, "Suite ([a-zA-Z]+)", "Suite \\1, "))
complete_results <- mutate(complete_results, Address = str_replace(Address,"suite ([a-zA-Z]+)", "Suite \\1, "))
complete_results <- mutate(complete_results, Address = str_replace(Address, "Ste ([a-zA-Z+])", "Suite \\1, "))
complete_results <- mutate(complete_results, Address = str_replace(Address, "Ste (\\d+)", "Suite \\1, "))
complete_results <- mutate(complete_results, Address = str_replace(Address, "MO-(\\d+)", "MO-\\1, "))
complete_results <- mutate(complete_results, Address = str_replace(Address, "US-(\\d+) E", "US-\\1 E, "))
complete_results <- mutate(complete_results, Address = str_replace(Address, "US-(\\d+)", "US-\\1, "))
complete_results <- mutate(complete_results, Address = str_replace(Address, "Rte (\\d+)", "Route \\1, "))
complete_results <- mutate(complete_results, Address = str_replace(Address, "#(\\d+)", "# \\1, "))
complete_results <- mutate(complete_results, Address = str_replace(Address,"St #([a-zA-Z]+)", "Suite \\1, "))

#Remove CSS tags
complete_results <- mutate(complete_results, Address = str_remove(Address, "<br />USA"))
complete_results <- mutate(complete_results, Address = str_remove(Address, "<br />United States"))
complete_results <- mutate(complete_results, Address = str_remove(Address, "<br />"))

#Remove prefix and suffix in the Descriptions to isolate business names
complete_results <- mutate(complete_results, Description = str_remove(Description, ".* at"))
complete_results <- mutate(complete_results, Description = str_remove(Description, "–.*"))

#Remove stray commas
complete_results <- mutate(complete_results, Description = str_remove(Description, " ., "))
```

Now add geocodes:
```{r}
#Use ggmap to geocode the addresses, throw them into the main data CSV.
#register_google(key="REDACTED") (You'll need your own Google API key to run this.)
locs <- geocode(complete_results$Address)

#Create temp variable column to match between the two tibbles
complete_results$common_id <- 1:nrow(complete_results)
locs$common_id <- 1:nrow(locs)

#Merge tibbles, delete temp variable
complete_results <- merge(complete_results, locs, by = "common_id", all = T)
complete_results <- complete_results[ , -1]
```


Only minor tweaks left to make in Excel for incorrectly-formatted submissions. Let's print this.
```{r}
write.csv(complete_results, "C:\\Users\\danmi\\Documents\\GitHub\\Data\\KC_Crypto_ATMs.csv", row.names=TRUE)
```
