---
title: "KC Crypto ATM Mapping"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
library(tidyverse)
library(tidycensus)
library(sf)
library(leaflet)
library(htmltools)
library(leaflet.extras)
library(htmlwidgets)

#Load ATM & bank data file
atms <- read.csv("C:\\Users\\danmi\\Documents\\GitHub\\Data\\KC_Crypto_ATMs.csv", header=TRUE)
bank_locs <-read.csv("c:\\Users\\danmi\\Documents\\GitHub\\Data\\KC_Bank_Locations.csv", header=TRUE)
```

We'll focus on on Jackson, Clay and Platte counties in Missouri and Johnson and Wyandotte counties in Kansas. Let's get the data from ACS. We're using the 2021 American Community Survey, the latest 5-Year.
```{r, include=FALSE}
#Grab variable list for most recent American Community Survey
v21 <- load_variables(2021, "acs5", cache = TRUE)
v21 <- v21 %>% filter(geography=="block group")

options(tigris_use_cache = TRUE)

#Pull data from Census API
mo_black <- get_acs(geography = "block group", 
                       variables = c("B02009_001"), 
                       year = 2021, 
                       survey = "acs5", 
                       state = "29",
                       geometry = TRUE)

ks_black <- get_acs(geography = "block group", 
                       variables = c("B02009_001"), 
                       year = 2021, 
                       survey = "acs5", 
                       state = "20",
                       geometry = TRUE)

mo_hispanic <- get_acs(geography = "block group", 
                       variables = c("B03003_003"), 
                       year = 2021, 
                       survey = "acs5", 
                       state = "29",
                       geometry = TRUE)

ks_hispanic <- get_acs(geography = "block group", 
                       variables = c("B03003_003"), 
                       year = 2021, 
                       survey = "acs5", 
                       state = "20",
                       geometry = TRUE)

mo_income <- get_acs(geography = "block group", 
                       variables = c("B19013_001"), 
                       year = 2021, 
                       survey = "acs5", 
                       state = "29",
                       geometry = TRUE)

ks_income <- get_acs(geography = "block group", 
                       variables = c("B19013_001"), 
                       year = 2021, 
                       survey = "acs5", 
                       state = "20",
                       geometry = TRUE)
```

Filter for counties of interest, merge paired MO/KS databases together
```{r}
#filter MO counties
mo_black <- mo_black %>% filter(grepl("Jackson|Clay|Platte", NAME))
mo_hispanic <- mo_hispanic %>% filter(grepl("Jackson|Clay|Platte", NAME))
mo_income <- mo_income %>% filter(grepl("Jackson|Clay|Platte", NAME))

#filter KS counties
ks_black <- ks_black %>% filter(grepl("Johnson|Wyandotte", NAME))
ks_hispanic <- ks_hispanic %>% filter(grepl("Johnson|Wyandotte", NAME))
ks_income <- ks_income %>% filter(grepl("Johnson|Wyandotte", NAME)) 

#bind together for cohesive KC map and shapefile
kc_black <- bind_rows(ks_black, mo_black)
kc_hispanic <- bind_rows(ks_hispanic, mo_hispanic)
kc_income <- bind_rows(ks_income, mo_income)

#align with datum requirements
kc_black <- st_transform(kc_black, crs = "+proj=longlat +datum=WGS84")
kc_hispanic <- st_transform(kc_hispanic, crs = "+proj=longlat +datum=WGS84")
kc_income <- st_transform(kc_income, crs = "+proj=longlat +datum=WGS84")
```
 
ATMs location vs. bank branches 
```{r}
kc_bank_map <- leaflet(
    options = leafletOptions(
      minZoom = 10,
      maxZoom = 14,
      dragging = TRUE
    )
  ) %>% 
  setView(
    lat = 39.1194,
    lng = -94.5766,
    zoom = 8
  ) %>% 
  setMaxBounds(
    lng1 = -94.5766 + 0.3,
    lat1 = 39.0925 + 0.3,
    lng2 = -94.5766 - 0.3,
    lat2 = 39.0925 - 0.3
   ) %>%  addCircles(
    lng = atms$lon, 
    lat = atms$lat,
    label = paste(atms$Description, atms$Address, atms$Install_Date, atms$Operator_Name, sep = ","),
    radius = 6,
    opacity = 1,
    color = "#ffc100"
  ) %>% addCircles(
    lng = bank_locs$lon,
    lat = bank_locs$lat,
    label = paste(bank_locs$Name, bank_locs$Address, sep = ",")
  ) %>% addProviderTiles(providers$CartoDB.Positron
  )
  
kc_bank_map
```

ATM locations vs. Black population
```{r}
kc_black_pal <- colorNumeric(palette = "viridis",
                    domain = kc_black$estimate, n = 20)

kc_black_map <- leaflet(
    options = leafletOptions(
      minZoom = 10,
      maxZoom = 15,
      dragging = TRUE
    )
  ) %>% 
  setView(
    lat = 39.1194,
    lng = -94.5766,
    zoom = 8
  ) %>% 
  setMaxBounds(
    lng1 = -94.5766 + 0.4,
    lat1 = 39.0925 + 0.4,
    lng2 = -94.5766 - 0.4,
    lat2 = 39.0925 - 0.4
  ) %>% 
  addPolygons(data = kc_black,
              stroke = FALSE,
              smoothFactor = 0,
              fillOpacity = 0.5,
              color = ~kc_black_pal(estimate)
   ) %>%  addCircles(
    lng = atms$lon, 
    lat = atms$lat,
    popup = paste0(
      "<strong>Location: </strong>",atms$Description, "<br>",
      "<strong>Address: </strong>",atms$Address, "<br>",
      "<strong>Install Date: </strong>",atms$Install_Date, "<br>",
      "<strong>Operator: </strong>",atms$Operator_Name, "<br>"),
    radius = 6,
    opacity = 1,
    color = "#ffc000"
  ) %>% 
  addTiles(
  ) %>% addLegend("bottomright", 
              pal = kc_black_pal, 
              values = kc_black$estimate,
              title = "Black population (est.)",
              opacity = 1)
  
kc_black_map

#saveWidget(kc_black_map, file = "KC_Crypto_Black_Pop.html")
```

ATM locations vs. Hispanic population
```{r}
kc_hispanic_pal <- colorNumeric(palette = "viridis",
                    domain = kc_hispanic$estimate, n = 20)

kc_hispanic_map <- leaflet(
    options = leafletOptions(
      minZoom = 10,
      maxZoom = 15,
      dragging = TRUE
    )
  ) %>% 
  setView(
    lat = 39.1194,
    lng = -94.5766,
    zoom = 8
  ) %>% 
  setMaxBounds(
    lng1 = -94.5766 + 0.4,
    lat1 = 39.0925 + 0.4,
    lng2 = -94.5766 - 0.4,
    lat2 = 39.0925 - 0.4
  ) %>% 
  addPolygons(data = kc_hispanic,
              stroke = FALSE,
              smoothFactor = 0,
              fillOpacity = 0.5,
              color = ~kc_hispanic_pal(estimate)
   ) %>%  addCircles(
    lng = atms$lon, 
    lat = atms$lat,
    popup = paste0(
      "<strong>Location: </strong>",atms$Description, "<br>",
      "<strong>Address: </strong>",atms$Address, "<br>",
      "<strong>Install Date: </strong>",atms$Install_Date, "<br>",
      "<strong>Operator: </strong>",atms$Operator_Name, "<br>"),
    radius = 3,
    opacity = 1,
    color = "#ffc000"
  ) %>% 
    addTiles(
  ) %>% addLegend("bottomright", 
              pal = kc_hispanic_pal, 
              values = kc_hispanic$estimate,
              title = "Hispanic/Latino population (est.)",
              opacity = 1)
  
kc_hispanic_map

#saveWidget(kc_hispanic_map, file = "KC_Crypto_Hispanic_Pop.html")
```

ATM locations vs. Median household income
```{r}
kc_income_pal <- colorNumeric(palette = "viridis",
                    domain = kc_income$estimate, n = 20)

kc_income_map <- leaflet(
    options = leafletOptions(
      minZoom = 10,
      maxZoom = 15,
      dragging = TRUE
    )
  ) %>% 
  setView(
    lat = 39.1194,
    lng = -94.5766,
    zoom = 8
  ) %>% 
  setMaxBounds(
    lng1 = -94.5766 + 0.3,
    lat1 = 39.0925 + 0.3,
    lng2 = -94.5766 - 0.3,
    lat2 = 39.0925 - 0.3
  ) %>% 
  addPolygons(data = kc_income,
              stroke = FALSE,
              smoothFactor = 0,
              fillOpacity = 0.5,
              color = ~kc_income_pal(estimate)
   ) %>%  addCircles(
    lng = atms$lon, 
    lat = atms$lat,
    popup = paste0(
      "<strong>Location: </strong>",atms$Description, "<br>",
      "<strong>Address: </strong>",atms$Address, "<br>",
      "<strong>Install Date: </strong>",atms$Install_Date, "<br>",
      "<strong>Operator: </strong>",atms$Operator_Name, "<br>"),
    radius = 6,
    opacity = 1,
    color = "#ffc000"
  ) %>% 
  addTiles(
  ) %>% 
  addLegend("bottomright", 
              pal = kc_income_pal, 
              values = kc_income$estimate,
              title = "Median Household Income",
              labFormat = labelFormat(prefix = "$"),
              opacity = 1)
  
kc_income_map

#saveWidget(kc_income_map, file = "KC_Crypto_Income_Map.html")
```

Foreign-born mapping
```{r}
#Pull data from Census API
mo_foreign <- get_acs(geography = "tract", 
                       variables = c("B05002_013"), 
                       year = 2021, 
                       survey = "acs5", 
                       state = "29",
                       geometry = TRUE)

ks_foreign <- get_acs(geography = "tract", 
                       variables = c("B05002_013"), 
                       year = 2021, 
                       survey = "acs5", 
                       state = "20",
                       geometry = TRUE)

#filter MO & KS counties
mo_foreign <- mo_foreign %>% filter(grepl("Jackson|Clay|Platte", NAME))
ks_foreign <- ks_foreign %>% filter(grepl("Johnson|Wyandotte", NAME))

#bind together for cohesive KC map and shapefile
kc_foreign <- bind_rows(ks_foreign, mo_foreign)

#align with datum requirements
kc_foreign <- st_transform(kc_foreign, crs = "+proj=longlat +datum=WGS84")
```


```{r}
kc_foreign_pal <- colorNumeric(palette = "viridis",
                    domain = kc_foreign$estimate, n = 20)

kc_foreign_map <- leaflet(
    options = leafletOptions(
      minZoom = 10,
      maxZoom = 15,
      dragging = TRUE
    )
  ) %>% 
  setView(
    lat = 39.1194,
    lng = -94.5766,
    zoom = 8
  ) %>% 
  setMaxBounds(
    lng1 = -94.5766 + 0.3,
    lat1 = 39.0925 + 0.3,
    lng2 = -94.5766 - 0.3,
    lat2 = 39.0925 - 0.3
  ) %>% 
  addPolygons(data = kc_foreign,
              stroke = FALSE,
              smoothFactor = 0,
              fillOpacity = 0.5,
              color = ~kc_foreign_pal(estimate)
   ) %>%  addCircles(
    lng = atms$lon, 
    lat = atms$lat,
     popup = paste0(
      "<strong>Location: </strong>",atms$Description, "<br>",
      "<strong>Address: </strong>",atms$Address, "<br>",
      "<strong>Install Date: </strong>",atms$Install_Date, "<br>",
      "<strong>Operator: </strong>",atms$Operator_Name, "<br>"),
    radius = 6,
    opacity = 1,
    color = "#ffc000"
  ) %>% 
  addTiles(
  ) %>% addLegend("bottomright", 
              pal = kc_foreign_pal, 
              values = kc_foreign$estimate,
              title = "Foreign-born population",
              opacity = 1)
  
kc_foreign_map
```
