---
title: "KC Crypto ATM Mapping"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
library(tidyverse)
library(tidycensus)
library(ggplot2)
library(ggmap)
library(sf)
library(leaflet)
library(htmltools)

#Load ATM data file
atms <- read.csv("C:\\Users\\danmi\\Documents\\GitHub\\Data\\KC_Crypto_ATMs.csv", header=TRUE)
```

We'll focus on on Jackson, Clay and Platte counties in Missouri and Johnson and Wyandotte counties in Kansas. Let's get the data from ACS. We're using the 2021 American Community Survey, the latest 5-Year.
```{r, include=FALSE}
#Grab variable list for most recent American Community Survey
v21 <- load_variables(2021, "acs5", cache = TRUE)
v21 <- v21 %>% filter(geography=="block group")


options(tigris_use_cache = TRUE)

#Pull data from Census API
mo_black <- get_acs(geography = "block group", 
                       variables = c("B02009_001"), 
                       year = 2021, 
                       survey = "acs5", 
                       state = "29",
                       geometry = TRUE)

ks_black <- get_acs(geography = "block group", 
                       variables = c("B02009_001"), 
                       year = 2021, 
                       survey = "acs5", 
                       state = "20",
                       geometry = TRUE)

mo_hispanic <- get_acs(geography = "block group", 
                       variables = c("B03003_003"), 
                       year = 2021, 
                       survey = "acs5", 
                       state = "29",
                       geometry = TRUE)

ks_hispanic <- get_acs(geography = "block group", 
                       variables = c("B03003_003"), 
                       year = 2021, 
                       survey = "acs5", 
                       state = "20",
                       geometry = TRUE)

mo_income <- get_acs(geography = "block group", 
                       variables = c("B19013_001"), 
                       year = 2021, 
                       survey = "acs5", 
                       state = "29",
                       geometry = TRUE)

ks_income <- get_acs(geography = "block group", 
                       variables = c("B19013_001"), 
                       year = 2021, 
                       survey = "acs5", 
                       state = "20",
                       geometry = TRUE)
```

Filter for counties of interest, merge paired MO/KS databases together
```{r}
#filer MO counties
mo_black <- mo_black %>% filter(grepl("Jackson|Clay|Platte", NAME))
mo_hispanic <- mo_hispanic %>% filter(grepl("Jackson|Clay|Platte", NAME))
mo_income <- mo_income %>% filter(grepl("Jackson|Clay|Platte", NAME))

#filter KS counties
ks_black <- ks_black %>% filter(grepl("Johnson|Wyandotte", NAME))
ks_hispanic <- ks_hispanic %>% filter(grepl("Johnson|Wyandotte", NAME))
ks_income <- ks_income %>% filter(grepl("Johnson|Wyandotte", NAME)) 

#bind together for cohesive KC map and shapefile
kc_black <- bind_rows(ks_black, mo_black)
kc_hispanic <- bind_rows(ks_hispanic, mo_hispanic)
kc_income <- bind_rows(ks_income, mo_income)

#align with datum requirements
kc_black <- st_transform(kc_black, crs = "+proj=longlat +datum=WGS84")
kc_hispanic <- st_transform(kc_hispanic, crs = "+proj=longlat +datum=WGS84")
kc_income <- st_transform(kc_income, crs = "+proj=longlat +datum=WGS84")
```

```{r}
kc_black_pal <- colorNumeric(palette = "viridis",
                    domain = kc_black$estimate, n = 20)

kc_black_map <- leaflet(
    options = leafletOptions(
      minZoom = 10,
      maxZoom = 14,
      dragging = TRUE
    )
  ) %>% 
  setView(
    lat = 39.1194,
    lng = -94.5766,
    zoom = 8
  ) %>% 
  setMaxBounds(
    lng1 = -94.5766 + 0.3,
    lat1 = 39.0925 + 0.3,
    lng2 = -94.5766 - 0.3,
    lat2 = 39.0925 - 0.3
  ) %>% 
  addPolygons(data = kc_black,
              stroke = FALSE,
              smoothFactor = 0,
              fillOpacity = 0.5,
              color = ~kc_black_pal(estimate)
   ) %>%  addCircles(
    lng = atms$lon, 
    lat = atms$lat,
    label = paste(atms$Description, atms$Address, atms$Install_Date, atms$Operator_Name, sep = ","),
    radius = 6,
    opacity = 1,
    color = "#ffc000"
  ) %>% 
  addTiles(
  ) %>% addLegend("bottomright", 
              pal = kc_black_pal, 
              values = kc_black$estimate,
              title = "Black population",
              opacity = 1)
  
kc_black_map
```

```{r}
kc_hispanic_pal <- colorNumeric(palette = "viridis",
                    domain = kc_hispanic$estimate, n = 20)

kc_hispanic_map <- leaflet(
    options = leafletOptions(
      minZoom = 10,
      maxZoom = 14,
      dragging = TRUE
    )
  ) %>% 
  setView(
    lat = 39.1194,
    lng = -94.5766,
    zoom = 8
  ) %>% 
  setMaxBounds(
    lng1 = -94.5766 + 0.3,
    lat1 = 39.0925 + 0.3,
    lng2 = -94.5766 - 0.3,
    lat2 = 39.0925 - 0.3
  ) %>% 
  addPolygons(data = kc_hispanic,
              stroke = FALSE,
              smoothFactor = 0,
              fillOpacity = 0.5,
              color = ~kc_hispanic_pal(estimate)
   ) %>%  addCircles(
    lng = atms$lon, 
    lat = atms$lat,
    label = paste(atms$Description, atms$Address, atms$Install_Date, atms$Operator_Name, sep = ","),
    radius = 3,
    opacity = 1,
    color = "#ffc000"
  ) %>% 
    addTiles(
  ) %>% addLegend("bottomright", 
              pal = kc_hispanic_pal, 
              values = kc_hispanic$estimate,
              title = "Hispanic/Latino population",
              opacity = 1)
  
kc_hispanic_map
```

```{r}
kc_income_pal <- colorNumeric(palette = "viridis",
                    domain = kc_income$estimate, n = 20)

kc_income_map <- leaflet(
    options = leafletOptions(
      minZoom = 10,
      maxZoom = 14,
      dragging = TRUE
    )
  ) %>% 
  setView(
    lat = 39.1194,
    lng = -94.5766,
    zoom = 8
  ) %>% 
  setMaxBounds(
    lng1 = -94.5766 + 0.3,
    lat1 = 39.0925 + 0.3,
    lng2 = -94.5766 - 0.3,
    lat2 = 39.0925 - 0.3
  ) %>% 
  addPolygons(data = kc_income,
              stroke = FALSE,
              smoothFactor = 0,
              fillOpacity = 0.5,
              color = ~kc_income_pal(estimate)
   ) %>%  addCircles(
    lng = atms$lon, 
    lat = atms$lat,
    label = paste(atms$Description, atms$Address, atms$Install_Date, atms$Operator_Name, sep = ","),
    radius = 6,
    opacity = 1,
    color = "#ffc000"
  ) %>% 
  addTiles(
  ) %>% 
  addLegend("bottomright", 
              pal = kc_income_pal, 
              values = kc_income$estimate,
              title = "Median Household Income",
              na.label = "",
              opacity = 1)
  
kc_income_map
```

EVERYTHING BELOW THIS LINE DOES NOT PLAY WELL WITH KNITR.
Maps look good, but let's get into the numbers. We need to join the datasets so we can locate the ATMs in specific block groups.
```{r, include=FALSE}
#Create matched dataset between ATM location and black population
kc_black_object <- st_as_sf(kc_black)
st_write(kc_black_object, "C:\\Users\\danmi\\Documents\\GitHub\\Data\\black_shape.shp")
kc_black_poly <- st_read("C:\\Users\\danmi\\Documents\\GitHub\\Data\\black_shape.shp")
kc_black_points <- st_as_sf(atms, coords = c("lon", "lat"), crs = st_crs(kc_black_poly))
kc_black_match <- st_join(kc_black_points, kc_black_poly)

#Create matched dataset between ATM location and median income of block group
kc_income_object <- st_as_sf(kc_income)
st_write(kc_income_object, "C:\\Users\\danmi\\Documents\\GitHub\\Data\\income_shape.shp")
kc_income_poly <- st_read("C:\\Users\\danmi\\Documents\\GitHub\\Data\\income_shape.shp")
kc_income_points <- st_as_sf(atms, coords = c("lon", "lat"), crs = st_crs(kc_income_poly))
kc_income_match <- st_join(kc_income_points, kc_income_poly)
```
Range analysis for income
```{r, include=FALSE}
sd(kc_income_match$estimate, na.rm = T)
min(kc_income_match$estimate, na.rm = T)
max(kc_income_match$estimate, na.rm = T)
IQR(kc_income_match$estimate, na.rm = T)

#We'll use $30k as the grouping amount since it's close to the standard deviation and IQR.

kc_income_range <- kc_income_match %>% mutate(range = case_when(
  estimate < 30000 ~ "sub_30",
  estimate >= 30000 & estimate <60000 ~ "30_60",
  estimate >= 60000 & estimate <90000 ~ "60-90",
  estimate >= 90000 & estimate <120000 ~ "90-120",
  estimate > 120000 ~ "120+",
  estimate > 80 ~ "80+",
))

kc_income_range %>% count(range)
```